Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-24 writeup/parkinsons.tex
Add bar plots of interpreted cluster vars

\documentclass[letterpaper,12pt]{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
% Random packages from
% http://tex.stackexchange.com/questions/50070/landscape-figure-in-latex
% Necessary for sideways pictures
\usepackage{wrapfig}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{epstopdf}
\usepackage{tablefootnote}
% \pagestyle{fancy}
% \lhead{Jesse Mu}
% \rhead{CSCI339 Term Project}
\graphicspath{ {../figures/} }

@@

\subsection{Decision Tree classifier based on clusters}

% CLUSTERS: 2
% ================================
% Root node error: 0.2573624
% Complexity Parameter: 0.01741294
% 10-fold CV error: 0.1241997
% CLUSTERS: 3
% ================================
% Root node error: 0.4571063
% Complexity Parameter: 0.0140056
% 10-fold CV error: 0.1766965
% CLUSTERS: 4
% ================================
% Root node error: 0.5236876
% Complexity Parameter: 0.01222494
% 10-fold CV error: 0.2535211
\begin{table}[ht]
  \centering
  \begin{tabular}{l|l|l|l|l|l}
    K & CP\tablefootnote{Complexity Parameter} & CV Xerror\tablefootnote{10-fold cross
    validation} & Root Feature &
    Root Error & Figure \\
    \hline
    2 & 0.017 & 0.124 & & 0.257 & Figure~\ref{fig:kmeans-dtree-2} \\
    3 & 0.014 & 0.177 & & 0.457 & Figure~\ref{fig:kmeans-dtree-3} \\
    4 & 0.012 & 0.254 & & 0.524 & Figure~\ref{fig:kmeans-dtree-4} \\
  \end{tabular}
  \caption{$k$-kmeans decision trees statistics}
  \label{tab:k-means-dtrees}
\end{table}

@@

\section{Biclustering}

>>>>

\documentclass[letterpaper,12pt]{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{numprint}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
% Random packages from
% http://tex.stackexchange.com/questions/50070/landscape-figure-in-latex
% Necessary for sideways pictures
\usepackage{wrapfig}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{epstopdf}
\usepackage{tablefootnote}
% for word wrap verbatim
\usepackage{listings}
\lstset{
   breaklines=true,
   basicstyle=\ttfamily}
% \pagestyle{fancy}
% \lhead{Jesse Mu}
% \rhead{CSCI339 Term Project}
\graphicspath{ {../figures/} }
% Or this, if run from main folder
% \graphicspath{ {./figures/} }

@@

\subsection{Cluster statistics}
% CLUSTERS: 2
% ================================
% Sizes: 201 580
% WithinSS: 4248.585 4132.434
% Sum WithinSS: 8381.019
% CLUSTERS: 3
% ================================
% Sizes: 420 231 130
% WithinSS: 2618.368 1973.82 3076.542
% Sum WithinSS: 7668.73
% CLUSTERS: 4
% ================================
% Sizes: 61 372 145 203
% WithinSS: 1481.25 1845.389 2147.988 1609.555
% Sum WithinSS: 7084.183
\begin{table}[ht]
  \centering
  \begin{tabular}{l|l|l|l}
    $k$ & $n$ & Within SS & sum(Within SS) \\
    \hline
    2 & 201/580 & 4248.585/4132.434 & 8381.019 \\
    3 & 420/231/130 & 2618.368/1973.82/3076.542 &  7668.73 \\
    4 & 61/372/145/203 & 1481.25/1845.389/2147.988/1609.555 & 7084.183
  \end{tabular}
  \caption{Cluster statistics}
  \label{tab:cluster-statistics}
\end{table}

\subsection{Decision trees based on clusters}
% seed = 911
% CLUSTERS: 2
% ================================
% Complexity Parameter: 0.03482587
% 10-fold CV error: 0.134443
% Root node error: 0.2573624
% CLUSTERS: 3
% ================================
% Complexity Parameter: 0.01
% 10-fold CV error: 0.1946223
% Root node error: 0.4622279
% CLUSTERS: 4
% ================================
% Complexity Parameter: 0.01
% 10-fold CV error: 0.2483995
% Root node error: 0.5236876
\begin{table}[ht]
  \centering
  \begin{tabular}{l|l|l|l|l|l}
    $k$ & CP\tablefootnote{Complexity Parameter} & CV Xerror\tablefootnote{10-fold cross
    validation} & Root Feature &
    Root Error & Figure \\
    \hline
    2 & 0.0348 & 0.134 & axial $\geq$ 0.44 & 0.257 & Figure~\ref{fig:kmeans-dtree-2} \\
    3 & 0.0100 & 0.194 & bradykin $<$ 0.0041 & 0.462 & Figure~\ref{fig:kmeans-dtree-3} \\
    4 & 0.0100 & 0.248 & bradykin $<$ 0.0041 & 0.523 & Figure~\ref{fig:kmeans-dtree-4} \\
  \end{tabular}
  \caption{$k$-kmeans decision trees statistics}
  \label{tab:k-means-dtrees}
\end{table}

@@

\subsection{Interpretation of Clusters}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{kmeans-summaries-2.pdf}
  \caption{Cluster Summaries, $k = 2$}
  \label{fig:kmeans-summaries-2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{kmeans-summaries-3.pdf}
  \caption{Cluster Summaries, $k = 3$}
  \label{fig:kmeans-summaries-3}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{kmeans-summaries-4.pdf}
  \caption{Cluster Summaries, $k = 4$}
  \label{fig:kmeans-summaries-4}
\end{figure}

\end{lstlisting}
\section{Biclustering}

Used BCBimax clustering algorithm. Clusters seem quite sparse.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{biclust-16.pdf}
  \caption{Biclustering $N = 16$}
  \label{fig:biclust-16}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{bubbleplot-16.pdf}
  \caption{Bubbleplot $N = 16$}
  \label{fig:bubbleplot-16}
\end{figure}
